---
title: "Reproducible Research: Peer Assessment 1"
output: 
html_document:
keep_md: true
---


## Loading and preprocessing the data

* Load the data
```{r echo=TRUE}
activity <- read.csv("activity.csv")
```
* Process/transform the data (if necessary) into a format suitable for your analysis
```{r echo=TRUE}
totalSteps <- aggregate(steps~date,data=activity,sum,na.rm=TRUE)
```

## What is mean total number of steps taken per day?

* Make a histogram of the total number of steps taken each day
```{r echo=TRUE}
hist(totalSteps$steps)
```

* Calculate and report the **mean** and **median** total number of steps taken 
per day 

```{r echo=TRUE}
mean(totalSteps$steps)
median(totalSteps$steps)
```
* The **mean** total number of steps taken per day is `r mean(totalSteps$steps)` steps.
* The **median** total number of steps taken per day is `r median(totalSteps$steps)` steps.

## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
